CAKE: Classification \textit{avec} Kernel Embeddings \\ using Rademacher Complexity Bounds

### 2017-07-09 cake.tex
Review first half of paper

	Positive definite symmetric kernels $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ are the soul of kernel methods, where they provide a coherent sense of similarity between two elements of the same space through implicitly defining higher dimensional features. However, they are most often selected by design, in which kernel based learning algorithms focus only on learning the weightings on the implicit features, and not the features itself. That is, the kernel itself is not learned. Multiple kernel learning has focused on learning constructions of richer kernels from simpler ones \citep{gonen2011multiple, zien2007multiclass}, although the simpler kernels themselves are also preselected by design. By placing a Gaussian process prior over the function class, Gaussian process models \citep{rasmussen2006gaussian} achieve tractable marginal likelihood based learning algorithms that is able to learn the model hyperparameters, which includes the kernel parameters. However, this approach requires various approximations for non-Gaussian likelihoods, and does not generalise well to non-Gaussian priors. Within the kernel embedding framework itself, hyperparameters have been similarly difficult to tune, and its learning is usually only restricted to heuristical approaches such as cross validation. Recent work has introduced Gaussian process priors on mean embeddings to achieve Bayesian hyperparameter learning \citep{flaxman2016bayesian}. However, the learning is separate from the application domain, and the approach has yet to generalise to conditional embeddings.

	In this paper, we take a learning theoretic approach to learn the hyperparameters of a conditional kernel embedding in a supervised manner. We begin by proposing the kernel embedding classifier (KEC), a principled framework for inferring multiclass probabilistic outputs using conditional embeddings, and provide a proof for its stochastic convergence. We then employ Rademacher complexity as a data dependent model complexity measure, and prove that expected classification risk can be bounded by empirical risk and conditional embedding trace norm with high probability. We use this bound to propose a learning objective that learns the balance between data fit and model complexity in a way that does not rely on priors.

@@

	We refer the reader to appendix B for proof. In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$. Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels (e.g. Mat\'{e}rn) with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$, for example, have $\alpha(\theta) = \sigma_{f}$. Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $X_{i}, Y_{i}$ are realised as the training observations $x_{i}, y_{i}$. We therefore employ this upper bound as the learning objective,
	\begin{equation}
		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\theta, \lambda}(x_{i})) + 4 e \; r(\theta, \lambda).
	\label{eq:learning_objective}
	\end{equation}
	We employ gradient based optimisers such as Gradient descent or Adam \citep{kingma2014adam}. Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, with the trade-off of relaxing bound tightness through $\sqrt{8 \log{(2 / \beta)} / n}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a subset of the training data. This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different upper bound of the generalisation risk. Because this bound holds with high probability over \textit{iid} samples, through randomly selecting a batch of training examples that comes from the same distribution, the resulting stochastic gradient will improve a strict upper bound with the same high probability. We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size. The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or other kernel data reduction technique to select data subsets that can estimate the already learned embedding. All further inference steps take $O(n^{2})$ time for back substitution.

>>>>

	Positive definite symmetric kernels $k : \mathcal{X} \times \mathcal{X} \to \mathbb{R}$ are the soul of kernel methods, where they provide a coherent sense of similarity between two elements of the same space through implicitly defining higher dimensional features. However, they are most often selected by design, in which kernel based learning algorithms focus only on learning the weightings on the implicit features, and not the features itself. That is, the kernel itself is not learned. Multiple kernel learning has focused on learning constructions of richer kernels from simpler ones \citep{gonen2011multiple, zien2007multiclass}, although the simpler kernels themselves are usually fixed a-priori. By placing a Gaussian process prior over the function class, Gaussian process models \citep{rasmussen2006gaussian} achieve tractable marginal likelihood based learning algorithms that is able to learn the model hyperparameters, which includes the kernel parameters. However, this approach requires various approximations for non-Gaussian likelihoods, and does not generalise well to non-Gaussian priors. Within the kernel embedding framework itself, hyperparameters have been similarly difficult to tune, and its learning is usually only restricted to heuristical approaches such as cross validation. Recent work has introduced Gaussian process priors on mean embeddings to achieve Bayesian hyperparameter learning \citep{flaxman2016bayesian}. However, the approach has yet to generalise to conditional embeddings for supervised learning.

	In this paper, we take a learning theoretic approach to learn the hyperparameters of a conditional kernel embedding in a supervised manner. We begin by proposing the kernel embedding classifier (KEC), a principled framework for inferring multiclass probabilistic outputs using conditional embeddings, and provide a proof for its stochastic convergence. We then employ Rademacher complexity as a data dependent model complexity measure, and prove that expected classification risk can be bounded by a combination of empirical risk and conditional embedding norm with high probability. We use this bound to propose a learning objective that learns the balance between data fit and model complexity in a way that does not rely on priors.

@@

	We refer the reader to appendix B for proof. In order for the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} to be non-trivial, we focus on bounded kernels in the sense that $\alpha^{2}(\theta) := \sup_{x \in \mathcal{X}} k_{\theta}(x, x) < \infty$. Gaussian kernels $k_{\theta}(x, x') = \sigma_{f}^{2} \exp{( - \frac{1}{2}(x - x') \Sigma^{-1} (x - x') )}$ and similar stationary kernels (e.g. Mat\'{e}rn) with sensitivity and length scales $\theta = (\sigma_{f}, \Sigma)$, for example, have $\alpha(\theta) = \sigma_{f}$. Since the training set itself is a sample of length $n$ drawn from $\mathbb{P}_{X Y}$, the inequality \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} is true with probability $1 - \beta$ when the random variables $X_{i}, Y_{i}$ are realised as the training observations $x_{i}, y_{i}$. We therefore employ this upper bound as the learning objective,
	\begin{equation}
		q(\theta, \lambda) := \frac{1}{n} \sum_{i = 1}^{n} \mathcal{L}_{\epsilon}(y_{i}, \bvec{f}_{\theta, \lambda}(x_{i})) + 4 e \; r(\theta, \lambda).
	\label{eq:learning_objective}
	\end{equation}
	We employ gradient based optimisers such as Gradient descent or Adam \citep{kingma2014adam}. Since \cref{thm:expected_risk_bound_hyperparameter_learning_copy} holds for any $n \in \mathbb{N}_{+}$ and any set of data $\{x_{i}, y_{i}\}_{i = 1}^{n}$ from $\mathbb{P}_{X Y}$, with the trade-off of relaxing bound tightness through $\sqrt{8 \log{(2 / \beta)} / n}$, the bound \eqref{eq:expected_risk_bound_hyperparameter_learning_copy} also holds with high probability for a subset of the training data. This enables scalable hyperparameter learning through batch stochastic gradient updates, where each gradient update stochastically improves a different upper bound of the generalisation risk. Because this bound holds with high probability over \textit{iid} samples, through randomly selecting a batch of training examples that comes from the same distribution, the resulting stochastic gradient will improve a strict upper bound with the same high probability. We present this scalable hyperparameter learning approach via batch stochastic gradient updates in \cref{alg:kernel_embedding_classifier_training}, reducing the time complexity from $O(n^{3})$ to $O(n_{b}^{3})$, where $n_{b}$ is the batch size. The Cholesky decomposition for the full training set requires $O(n^{3})$ time and is performed only once after learning instead of once every learning iteration, and can be avoided by using kernel herding \citep{chen2010super} or random Fourier features \citep{rahimi2008random} to estimate the already learned embedding. All further inference steps take $O(n^{2})$ time for back substitution.
